CHEC Study Sweat Chloride

### 2024-05-17 Edith Zemanick/Sweat Test/sweat_test_analysis_chec.qmd
added pre-modulator correlations

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = `Sweat Chloride Group`)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~`Sweat Chloride Group`, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = Diagnosis)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~Diagnosis, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = geno_class)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~geno_class, scales = "free", ncol = 2)
```

@@

```{r data cleaning}
# Import CHEC data
chec <- read.csv("./Data_Raw/CHEC sweat sodium and chloride.csv")
# Chloride groups
chec$swc_group <- cut(chec$swcavg, c(-Inf, 30, 60, Inf),
  right = F,
  labels = c("< 30", "30-59", ">60")
)
```

@@

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = swc_group)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~swc_group, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = genotype_group)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha=0.2) +
  stat_poly_line(se=F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~genotype_group, scales = "free", ncol = 2)
```

>>>>

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = `Sweat Chloride Group`)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~`Sweat Chloride Group`, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = Diagnosis)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~Diagnosis, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(df, aes(x = Na, y = Cl, colour = geno_class)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(df, aes(x = Na, y = Cl)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~geno_class, scales = "free", ncol = 2)
```

@@

```{r data cleaning}
# Import CHEC data
chec <- read.csv("./Data_Raw/CHEC sweat sodium and chloride.csv")
# Chloride groups
chec$swc_group <- cut(chec$swcavg, c(-Inf, 30, 60, Inf),
  right = F,
  labels = c("< 30", "30-59", ">60")
)
chec$swc_group_pm <- cut(chec$swhcavgpm, c(-Inf, 30, 60, Inf),
  right = F,
  labels = c("< 30", "30-59", ">60")
)
```

# Pre-modulator

@@

```{r}
#| warning: false
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm, colour = swc_group_pm)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~swc_group_pm, scales = "free", ncol = 2)
```

@@

```{r}
#| warning: false
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm, colour = genotype_group)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~genotype_group, scales = "free", ncol = 2)
```

```{r}
#| warning: false
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm, colour = genotype_group)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swhsavgpm, y = swhcavgpm)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~genotype_group, scales = "free", ncol = 2)
```

# Post-modulator

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = swc_group)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~swc_group, scales = "free", ncol = 2)
```

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = genotype_group)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~genotype_group, scales = "free", ncol = 2)
```

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = genotype_group)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~genotype_group, scales = "free", ncol = 2)
```

## By modulator type

```{r}
#| warning: false
ggplot(chec, aes(x = swsavg, y = swcavg, colour = modqual)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw()
ggplot(chec, aes(x = swsavg, y = swcavg)) +
  geom_point(alpha = 0.2) +
  stat_poly_line(se = F) +
  stat_poly_eq(use_label(c("eq", "R2"))) +
  theme_bw() +
  facet_wrap(~modqual, scales = "free", ncol = 2)
```
